\speculake: Hiding Malware in Speculative Execution

### 2018-05-07 paper/figures.tex
Read through - minor updates
add caption for high-level

\begin{figure}[ht]
    \centering
    % \includegraphics[clip, trim=6cm 13.5cm 3.8cm 5cm, width=0.9\linewidth]{figures/exspectre-high-level.pdf}
    \includegraphics[width=0.9\linewidth]{figures/exspectre-high-level-trimmed.pdf}
    \caption{\textbf{Exspectre}\,---\, %
    1, 2, 3, 4...}

@@

\newcommand{\FigCacheMiss}{
\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/cache_miss_dist}
    \caption{Cache Hit/Miss Latency Distribution}
    \label{fig:cache-miss}
\end{figure}
}

>>>>

\begin{figure}[ht]
    \centering
    % \includegraphics[clip, trim=6cm 13.5cm 3.8cm 5cm, width=0.9\linewidth]{figures/exspectre-high-level.pdf}
    \includegraphics[width=0.9\linewidth]{figures/exspectre-high-level-trimmed.pdf}
    \caption{\textbf{\speculake}\,---\,%
    Both the Trigger and Payload binaries exhibit the same initial series of
    indirect jumps, shown in Step 1. The trigger program solely executes these
    jumps to (mis)train the branch predictor. In the Payload program
    \texttt{fn\_ptr} has been set to point to the \texttt{cache\_timing}
    function and flushed from cache. Thus at Step 2 the branch predictor
    mis-predicts the jump to \texttt{cache\_timing} and instead jumps to
    \texttt{target\_fn} as trained by the Trigger program (green line). 
    \texttt{target\_fn} then executes speculatively as shown in Step 3. 
    Eventually \texttt{fn\_ptr} is loaded from memory and this mis-jump is 
    recognized by the processor, directing computation to Step 4, the 
    \texttt{cache\_timing} function, which then computes which value was loaded 
    into cache speculatively.}

@@

\newcommand{\FigCacheMiss}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/cache_miss_dist}
    \caption{Cache Hit/Miss Latency Distribution}
    \label{fig:cache-miss}
\end{figure}
}
